```{r}
options(digits = 3) # by default, print results to three decimal digits

library(tidyverse)
library(gridExtra) # for multiple ggplots in one window
library(gt)        # grammar of tables
library(xml2)      # save formatted tables as rtf 
library(reshape2)  # for melt() function
library(rtdists)  # DDM functions rdiffusion(), ddiffusion(), qdiffusion()
library(lme4)
library(lmerTest)
library(modelbased)
library(patchwork)
library(effectsize)
library(parameters)
library(rempsyc)
library(flextable)
```

### Load data

```{r}
experiment_data <- read_csv("Data/clean_data/experiment_data.csv", show_col_types = FALSE)
experiment_data$ID <- factor(experiment_data$ID)
experiment_data$Evaluation <- factor(experiment_data$Evaluation)
experiment_data$CL <- factor(experiment_data$CL, levels = c("low","high"))
experiment_data$block <- factor(experiment_data$block)
experiment_data$trial_block <- factor(experiment_data$trial_block)
```

### Define LL optimisation function

```{r}
ll_diffusion <- function(pars, datlist)
{
  loss=0
  for (myVar in 1:length(datlist))
    loss = loss - sum(log(ddiffusion(datlist[[myVar]],
                                     a=pars[1], v=pars[3+myVar], t0=pars[2], z=pars[3])))
  return(loss)  # return -LL
}
```

# DDM and recovery study for all participants

### Prepare data and initialise a model with 5 parameters

```{r}
set.seed(42)

data <- experiment_data[,c("ID","Target","Errors","RT_Raw","CL_evaluation")]
data <- data %>% filter(!is.na(RT_Raw))

data <- mutate(data, response = case_when(
  (Target==0 & Errors==0) ~ "lower",
  (Target==0 & Errors==1) ~ "upper",
  (Target==1 & Errors==0) ~ "upper",
  (Target==1 & Errors==1) ~ "lower" ))

ddm.df <- data.frame(
  ID = data$ID,
  rt = data$RT_Raw,
  response = as.factor(data$response),
  cond = data$Target,
  CL_Eval = data$CL_evaluation)


###
ID_list <- unique(subset(ddm.df, !(ID %in% c("40122", "511327", "765713")))[,"ID"])
#ID_list <- unique(ddm.df$ID)
conditions = unique(ddm.df$CL_Eval)

p_ddm5 <- c(1, 0.1, 0.5, 0, 0) # starting values with two drift rates
names(p_ddm5) <- c("a", "t0", "z", "v1","v2")

n_conditions <- 4
n_parameters <- 5

ddm_list <- list()

```

### run models

```{r}
ddm.df$response <- relevel(ddm.df$response, ref="lower") # lower is reference level

for (participant in ID_list){   # loop through each participant
  
  sub_df <- subset(ddm.df, ID == participant)

  DDM5 <- data.frame(matrix(NA, nrow=n_conditions, ncol=n_parameters+10))
  names(DDM5) <- c("ID", "condition", "Ns1", "Ns2", "acc", "M_rt", "a", "z", "v1", "v2", "t0", "converge", "-LLE", "AIC", "BIC")
  
  for (i in 1:length(conditions)){    # loop through conditions inside each participant
    
    df <- subset(sub_df, CL_Eval == conditions[i])
    # subset the data into sublists for the two trial types (conditions)
    data1.s1 = subset(df, cond==0)
    data1.s2 = subset(df, cond==1)
    data1.both = list(data1.s1, data1.s2)
  
    results <- optim(par=p_ddm5, f=ll_diffusion, dat=data1.both, method="Nelder-Mead", control = c(maxit = 2000))
    
    parms <- results$par
    DDM5[i, "ID"] <- participant
    DDM5[i,"condition"] <- conditions[i]
    DDM5[i, "Ns1"] <- nrow(subset(df, cond == 0))
    DDM5[i, "Ns2"] <- nrow(subset(df, cond==1))
    DDM5[i,"acc"] <- (table(df$cond, df$resp)[1,1] + table(df$cond, df$resp)[2,2]) / nrow(df)
    DDM5[i,"M_rt"] <- mean(df$rt)
    DDM5[i,"a"] <- parms["a"]
    DDM5[i,"t0"] <- parms["t0"]
    DDM5[i,"v1"] <- parms["v1"]
    DDM5[i,"v2"] <- parms["v2"]
    DDM5[i, "z"] <- (parms["z"] / parms["a"])
    DDM5[i, "converge"] <- results$convergence
    DDM5[i,"-LLE"] <- results$value
    DDM5[i, "AIC"] <- 2*n_parameters - 2*-1*results$value
    DDM5[i, "BIC"] <- n_parameters*log(DDM5[i, "Ns1"] + DDM5[i, "Ns2"]) - 2*-1*results$value
  
  }

  
  ## Generate recovery study and safe the values in the same data.frame
  pred_df <- data.frame(matrix(NA, nrow=n_conditions, ncol=n_parameters+4))
  names(pred_df) <- c("sep", "p.acc", "p.M_rt", "p.a", "p.z", "p.v1", "p.v2", "p.t0", "p.convergence")
  DDM5 <- cbind(DDM5,pred_df)
  
  ###
  # lower == non-target == s1
  # upper == target == s2
  
  
  for (i in 1:length(conditions)){
    
    
    parm_recov_s1 <- cbind(rdiffusion(n=DDM5[i,"Ns1"],
                                   a=DDM5$a[i],
                                   t0=DDM5$t0[i],
                                   z=DDM5$z[i],
                                   v=DDM5$v1[i]), cond=0)
    parm_recov_s2 <- cbind(rdiffusion(n=DDM5[i,"Ns2"],
                                   a=DDM5$a[i],
                                   t0=DDM5$t0[i],
                                   z=DDM5$z[i],
                                   v=DDM5$v2[i]), cond=1)
    
    parm_recov <- rbind(parm_recov_s1, parm_recov_s2)
    parm_recov.both <- list(subset(parm_recov, cond==0), subset(parm_recov, cond==1))
    
    
    sim <- optim(par=p_ddm5, f=ll_diffusion, dat=parm_recov.both, method="Nelder-Mead", control = c(maxit = 2000))
    
    parms <- sim$par
    DDM5[i,"p.acc"] <- (table(parm_recov$cond, parm_recov$resp)[2,2] + table(parm_recov$cond, parm_recov$resp)[1,1]) / nrow(parm_recov)
    DDM5[i,"p.M_rt"] <- mean(parm_recov$rt)
    DDM5[i,"p.a"] <- parms["a"]
    DDM5[i,"p.t0"] <- parms["t0"]
    DDM5[i,"p.v1"] <- parms["v1"]
    DDM5[i,"p.v2"] <- parms["v2"]
    DDM5[i, "p.z"] <- parms["z"] / parms["a"]
    DDM5[i, "p.converge"] <- sim$convergence
  
  }
  
  ddm_list <- append(ddm_list, list(DDM5))  
  
}

```

### merge indivudal dfs

```{r}
rtdist_df <- do.call(rbind, ddm_list)

sum(rtdist_df$converge/nrow(rtdist_df))
sum(rtdist_df$p.converge/nrow(rtdist_df))

write_csv(rtdist_df, "Data/clean_data/ddm_df.csv")
```

### correlation between estimated and recovered parameters

```{r}
recov_cor <- data.frame(
  parameter = c("acc", "M.rt", "a", "t0", "v1", "v2", "z"),
  corr = c(cor(rtdist_df$acc, rtdist_df$p.acc),   
           cor(rtdist_df$M_rt, rtdist_df$p.M_rt),
           cor(rtdist_df$a, rtdist_df$p.a),   # boundary / speed-acc trade-off
           cor(rtdist_df$t0, rtdist_df$p.t0),   # non-decision time
           cor(rtdist_df$v1, rtdist_df$p.v1),   # drift rate response non-target 0
           cor(rtdist_df$v2, rtdist_df$p.v2),   # drift rate response target 1
           cor(rtdist_df$z, rtdist_df$p.z)   # bias
  )
)

table <- nice_table(recov_cor, 
                    title = c("Table S4", "Recovery Study for Estimated DDM Parameters"),
                    note = c(
                      "DDM = drift diffusion model; r > .75 is considered good, r > .95 is consideered excellent. Note that the correlation for the bias parameter z suggests an insufficient reliability."
                    ))

save_as_docx(table, path = "TablesFigures/Table S4 - DDM recov study.docx")
```

------------------------------------------------------------------------

# Group level analyses

```{r}
rtdist_df <- read_csv("Data/clean_data/ddm_df.csv", show_col_types = FALSE)
```


```{r}
main_df <- rtdist_df[,c("ID","condition", "a","z","v1","v2")]
main_df$CL <- factor(ifelse(grepl("low", main_df$condition),
                      "low", "high"), levels = c("low","high"))
main_df$Eval <- factor(ifelse(grepl("0", main_df$condition),
                      0, 1))
levels(main_df$CL); levels(main_df$Eval)
```

## Speed-accuracy trade-off (boundary a)

```{r}
m1 <- lmer(scale(a) ~ CL*Eval + (1|ID), data = main_df, REML = T)
m2 <- lmer(scale(a) ~ CL+Eval + (1|ID), data = main_df, REML = T)
AIC(m1)-AIC(m2)
BIC(m1)-BIC(m2)

m3 <- lmer(scale(a) ~ z + v1 + v2 + CL+Eval + (1|ID), data = main_df, REML = T)
AIC(m3)-AIC(m2)
BIC(m3)-BIC(m2)

# unstandardized
model_parameters(m2)



```

```{r}
table <- model_parameters(lmer(scale(a) ~ CL+Eval + (1|ID), data = main_df, REML = T))[1:3,] %>% dplyr::select(c("Parameter","Coefficient", "SE", "CI_low", "CI_high", "p"))

table <- nice_table(table, 
                    title = c("Table S5", "LMM a"),
                    note = c(
                      "* p < .05, ** p < .01, *** p < .001. CL = Cognitive Load; CI = Confidence Interval."
                    ))

save_as_docx(table, path = "TablesFigures/Table S5 - DDM a.docx")
```

```{r, fig.width=7, fig.height=5}
emm_mod <- lmer(scale(a) ~ CL*Eval + (1|ID), data = main_df, REML = T)
emm <- estimate_means(emm_mod, ~CL*Eval)

plot_a <- ggplot(emm, aes(x = Eval, y = Mean, group = factor(CL), color=factor(CL),shape=CL, linetype = factor(CL))) +
  geom_point(position = position_dodge(width = 0.2), size = 2.5) +
  geom_line(position = position_dodge(width = 0.2), linewidth = 0.5) +
  geom_errorbar(aes(ymin=CI_low, ymax=CI_high), width=.2,
                position=position_dodge(0.2),linewidth=0.35,linetype=1)+
  labs(x = "Social Evaluation", y = "a (Boundary)",
       color = "Cognitive Load", shape="Cognitive Load", linetype="Cognitive Load") +
  
  scale_x_discrete(labels = c("control", "evaluation"))+
  
  theme_classic() +

  scale_shape_manual(values = c(15, 19),
                     labels = c("low", "high")) +  # Use square for H0 and circle for H1
  scale_color_manual(values = c("lightskyblue4", "lightsalmon"),
                     labels = c("low", "high")) +  # Orange color for H0 and dark green for H1
  scale_linetype_manual(values = c(1,2),
                       labels = c("low", "high")) +
  
  #theme_classic() +
  theme(legend.text = element_text(size = 8),
        axis.title.x = element_text(vjust = -3),
        axis.title.y = element_text(vjust = 3),
        plot.margin = margin(b = 15, l=15))

```

No differences in speed-accuracy trade-off

## Bias

```{r}
m1 <- lmer(scale(z) ~ CL*Eval + (1|ID), data = main_df, REML = T)
m2 <- lmer(scale(z) ~ CL+Eval + (1|ID), data = main_df, REML = T)
AIC(m1)-AIC(m2)
BIC(m1)-BIC(m2)

m3 <- lmer(scale(z) ~ scale(a) + scale(v1) + scale(v2) + CL+Eval + (1|ID), data = main_df, REML = T)
AIC(m3)-AIC(m2)
BIC(m3)-BIC(m2)

model_parameters(m3)

```

```{r}
table <- model_parameters(m3) %>% filter(Parameter %in% c("(Intercept)", "CLhigh", "Eval1")) %>% dplyr::select(c("Parameter","Coefficient", "SE", "CI_low", "CI_high", "p"))

table <- nice_table(table, 
                    title = c("Table S5", "LMM z"),
                    note = c(
                      "* p < .05, ** p < .01, *** p < .001. CL = Cognitive Load; CI = Confidence Interval."
                    ))

save_as_docx(table, path = "TablesFigures/Table S5 - DDM z.docx")
```

```{r}
emm_mod <- lmer(scale(z) ~ scale(a) + scale(v1) + scale(v2) + CL*Eval + (1|ID), data = main_df, REML = T)
emm <- estimate_means(emm_mod, ~CL*Eval)

plot_z <- ggplot(emm, aes(x = Eval, y = Mean, group = factor(CL), color=factor(CL),shape=CL, linetype = factor(CL))) +
  geom_point(position = position_dodge(width = 0.2), size = 2.5) +
  geom_line(position = position_dodge(width = 0.2), linewidth = 0.5) +
  geom_errorbar(aes(ymin=CI_low, ymax=CI_high), width=.2,
                position=position_dodge(0.2),linewidth=0.35,linetype=1)+
  labs(x = "Social Evaluation", y = "z (Bias)",
       color = "Cognitive Load", shape="Cognitive Load", linetype="Cognitive Load") +
  
  scale_x_discrete(labels = c("control", "evaluation"))+
  
  theme_classic() +

  scale_shape_manual(values = c(15, 19),
                     labels = c("low", "high")) +  # Use square for H0 and circle for H1
  scale_color_manual(values = c("lightskyblue4", "lightsalmon"),
                     labels = c("low", "high")) +  # Orange color for H0 and dark green for H1
  scale_linetype_manual(values = c(1,2),
                       labels = c("low", "high")) +
  
  #theme_classic() +
  theme(legend.text = element_text(size = 8),
        axis.title.x = element_text(vjust = -3),
        axis.title.y = element_text(vjust = 3),
        plot.margin = margin(b = 15, l=15))

```

Significant differences between Evaluation conditions

## v1 (information accumulation speed for non-target responses)

```{r}
m1 <- lmer(scale(v1) ~ CL*Eval + (1|ID), data = main_df, REML = T)
m2 <- lmer(scale(v1) ~ CL+Eval + (1|ID), data = main_df, REML = T)
AIC(m1)-AIC(m2)
BIC(m1)-BIC(m2)

m3 <- lmer(scale(v1) ~ scale(a) + scale(z) + scale(v2) + CL+Eval + (1|ID), data = main_df, REML = T)
AIC(m3)-AIC(m2)
BIC(m3)-BIC(m2)


summary(m3)
```

```{r}
table <- model_parameters(m3) %>% filter(Parameter %in% c("(Intercept)", "CLhigh", "Eval1")) %>% dplyr::select(c("Parameter","Coefficient", "SE", "CI_low", "CI_high", "p"))

table <- nice_table(table, 
                    title = c("Table S5", "LMM v1"),
                    note = c(
                      "* p < .05, ** p < .01, *** p < .001. CL = Cognitive Load; CI = Confidence Interval."
                    ))

save_as_docx(table, path = "TablesFigures/Table S5 - DDM v1.docx")
```

```{r}
emm_mod <- lmer(scale(v1) ~ scale(a) + scale(z) + scale(v2) + CL*Eval + (1|ID), data = main_df, REML = T)
emm <- estimate_means(emm_mod, ~CL*Eval)

plot_v1 <- ggplot(emm, aes(x = Eval, y = Mean, group = factor(CL), color=factor(CL),shape=CL, linetype = factor(CL))) +
  geom_point(position = position_dodge(width = 0.2), size = 2.5) +
  geom_line(position = position_dodge(width = 0.2), linewidth = 0.5) +
  geom_errorbar(aes(ymin=CI_low, ymax=CI_high), width=.2,
                position=position_dodge(0.2),linewidth=0.35,linetype=1)+
  labs(x = "Social Evaluation", y = "v1 (Drift rate)",
       color = "Cognitive Load", shape="Cognitive Load", linetype="Cognitive Load") +
  
  scale_x_discrete(labels = c("control", "evaluation"))+
  
  theme_classic() +

  scale_shape_manual(values = c(15, 19),
                     labels = c("low", "high")) +  # Use square for H0 and circle for H1
  scale_color_manual(values = c("lightskyblue4", "lightsalmon"),
                     labels = c("low", "high")) +  # Orange color for H0 and dark green for H1
  scale_linetype_manual(values = c(1,2),
                       labels = c("low", "high")) +
  
  #theme_classic() +
  theme(legend.text = element_text(size = 8),
        axis.title.x = element_text(vjust = -3),
        axis.title.y = element_text(vjust = 3),
        plot.margin = margin(b = 15, l=15))

```

## v2 (information accumulation speed for target responses)

```{r}
m1 <- lmer(scale(v2) ~ CL*Eval + (1|ID), data = main_df, REML = T)
m2 <- lmer(scale(v2) ~ CL+Eval + (1|ID), data = main_df, REML = T)
AIC(m1)-AIC(m2)
BIC(m1)-BIC(m2)

m3 <- lmer(scale(v2) ~ scale(a) + scale(z) + scale(v1) + CL+Eval + (1|ID), data = main_df, REML = T)
AIC(m3)-AIC(m2)
BIC(m3)-BIC(m2)


summary(m3)
```

```{r}
table <- model_parameters(m3) %>% filter(Parameter %in% c("(Intercept)", "CLhigh", "Eval1")) %>% dplyr::select(c("Parameter","Coefficient", "SE", "CI_low", "CI_high", "p"))

table <- nice_table(table, 
                    title = c("Table S5", "LMM v2"),
                    note = c(
                      "* p < .05, ** p < .01, *** p < .001. CL = Cognitive Load; CI = Confidence Interval."
                    ))

save_as_docx(table, path = "TablesFigures/Table S5 - DDM v2.docx")
```

```{r}
emm_mod <- lmer(scale(v2) ~ scale(a) + scale(z) + scale(v1) + CL*Eval + (1|ID), data = main_df, REML = T)
emm <- estimate_means(emm_mod, ~CL*Eval)

plot_v2 <- ggplot(emm, aes(x = Eval, y = Mean, group = factor(CL), color=factor(CL),shape=CL, linetype = factor(CL))) +
  geom_point(position = position_dodge(width = 0.2), size = 2.5) +
  geom_line(position = position_dodge(width = 0.2), linewidth = 0.5) +
  geom_errorbar(aes(ymin=CI_low, ymax=CI_high), width=.2,
                position=position_dodge(0.2),linewidth=0.35,linetype=1)+
  labs(x = "Social Evaluation", y = "v2 (Drift rate)",
       color = "Cognitive Load", shape="Cognitive Load", linetype="Cognitive Load") +
  
  scale_x_discrete(labels = c("control", "evaluation"))+
  
  theme_classic() +

  scale_shape_manual(values = c(15, 19),
                     labels = c("low", "high")) +  # Use square for H0 and circle for H1
  scale_color_manual(values = c("lightskyblue4", "lightsalmon"),
                     labels = c("low", "high")) +  # Orange color for H0 and dark green for H1
  scale_linetype_manual(values = c(1,2),
                       labels = c("low", "high")) +
  
  #theme_classic() +
  theme(legend.text = element_text(size = 8),
        axis.title.x = element_text(vjust = -3),
        axis.title.y = element_text(vjust = 3),
        plot.margin = margin(b = 15, l=15))

```

**merge images**

```{r, fig.width=7, fig.height=5}

combined_plot <- ((plot_a | plot_z) / (plot_v1 | plot_v2)) +
  plot_annotation(tag_levels = 'A') +
  plot_layout(guides = "collect") &
  theme(plot.tag = element_text(face = "bold"),
        legend.position='bottom')

# Display the combined plot
print(combined_plot)
ggsave("TablesFigures/Figure S1 - DDM_results.jpeg",dpi=600, w= 7, h = 5)
```
