**Import libraries using a reproducible approach**

```{r}
pkgs <- c("tidyverse",
          "rempsyc",
          "flextable",
          "plyr",
          "lattice",
          "tidyverse",
          "Rmisc",
          "cowplot",
          "devtools",
          "gghalves",
          "car",
          "readxl",
          "patchwork")

lapply(pkgs, library, character.only=TRUE)

```

```{r}
C_pallette = c("#FED789", "#476F84", "#453947")
c1_low = "#FED789"
c2_high = "#476F84"
c3 = "#453947"
```

### Load data

```{r}
TLX_and_ADES <- read_csv("Data/clean_data/TLX_and_ADES_clean.csv", show_col_types = FALSE)
PostExp <- read_csv("Data/clean_data/PostExp_clean.csv", show_col_types = FALSE)
agg_df <- read_csv("Data/clean_data/agg_df.csv", show_col_types = FALSE)
main_df <- read_csv("Data/clean_data/main_df.csv", show_col_types = FALSE)
```

### Data Preparation

```{r}
main_df <- read_csv("Data/clean_data/main_df.csv", show_col_types = FALSE)
main_df$ID <- factor(main_df$ID)
main_df$Evaluation <- factor(main_df$Evaluation)
main_df$CL <- factor(main_df$CL, levels = c("low","high"))
main_df$block <- factor(main_df$block)
main_df$trial_block <- factor(main_df$trial_block)

agg_df <- read_csv("Data/clean_data/agg_df.csv", show_col_types = FALSE)
agg_df$ID <- factor(agg_df$ID)
agg_df$Evaluation <- factor(agg_df$Evaluation)
agg_df$CL <- factor(agg_df$CL,levels = c("low","high"))

TLX_and_ADES <- read_csv("Data/clean_data/TLX_and_ADES_clean.csv", show_col_types = FALSE)
TLX_and_ADES$ID <- factor(TLX_and_ADES$ID)
TLX_and_ADES$Evaluation <- factor(TLX_and_ADES$Evaluation)
TLX_and_ADES$CL <- factor(TLX_and_ADES$CL,levels = c("low","high"))

PostExp <- read_csv("Data/clean_data/PostExp_clean.csv", show_col_types = FALSE)
```

## 

# Descriptive Statistics

## Demographics

Sex

```{r}
paste("N women =", as.numeric(PostExp %>% filter(Sex==2) %>% dplyr::summarise(n())))

paste("N men =", as.numeric(PostExp %>% filter(Sex==1) %>% dplyr::summarise(n())))
```

Age

```{r}
PostExp %>%
  dplyr::summarise(M = mean(Age), SD = sd(Age),
                   min = min(Age), max = max(Age), n = n()) %>% data.frame()

PostExp %>% select(Age) %>% count() %>%
  mutate( "%" = round(freq / sum(freq) * 100))
```

## Working Memory Performance

Errors

```{r}
descriptives <- agg_df %>% group_by(Evaluation, CL) %>% 
  dplyr::summarise(M = mean(Errors,na.rm = TRUE), SD = sd(Errors,na.rm = TRUE), n = n()) %>% 
  mutate(SE = SD / sqrt(n),
         CI_lower = M - qt(1 - (0.05 / 2), n - 1) * SE,
         CI_upper = M + qt(1 - (0.05 / 2), n - 1) * SE)

descriptives_Errors <- cbind(descriptives[,1:2],round(descriptives[,3:8],2))
descriptives_Errors

descriptives <- main_df %>% group_by(Evaluation, CL, block, trial_block) %>% 
  dplyr::summarise(M = mean(Errors,na.rm = TRUE), SD = sd(Errors,na.rm = TRUE), n = n()) %>% 
  mutate(SE = SD / sqrt(n),
         CI_lower = M - qt(1 - (0.05 / 2), n - 1) * SE,
         CI_upper = M + qt(1 - (0.05 / 2), n - 1) * SE)

descriptives_Errors_all <- cbind(descriptives[,1:4],round(descriptives[,5:10],2))
descriptives_Errors_all
```

Omission errors

```{r}
agg_df %>% group_by(ID) %>% select(oER) %>% count() %>%
  mutate( "%" = round(freq / sum(freq) * 100))
```

Reaction Time

```{r}
descriptives <- agg_df %>% group_by(Evaluation, CL) %>% 
  dplyr::summarise(M = mean(RT_Raw,na.rm = TRUE), SD = sd(RT_Raw,na.rm = TRUE), n = n()) %>% 
  mutate(SE = SD / sqrt(n),
         CI_lower = M - qt(1 - (0.05 / 2), n - 1) * SE,
         CI_upper = M + qt(1 - (0.05 / 2), n - 1) * SE)

descriptives_RT_Raw <- cbind(descriptives[,1:2],round(descriptives[,3:8],2))
descriptives_RT_Raw


descriptives <- main_df %>% group_by(Evaluation, CL, block, trial_block) %>% 
  dplyr::summarise(M = mean(RT_Raw,na.rm = TRUE), SD = sd(RT_Raw,na.rm = TRUE), n = n()) %>% 
  mutate(SE = SD / sqrt(n),
         CI_lower = M - qt(1 - (0.05 / 2), n - 1) * SE,
         CI_upper = M + qt(1 - (0.05 / 2), n - 1) * SE)

descriptives_RT_Raw_all <- cbind(descriptives[,1:4],round(descriptives[,5:10],2))
descriptives_RT_Raw_all
```

*Merge descriptives*

```{r}
## Across Evaluation and CL
c_names <- colnames(descriptives_RT_Raw)[-1:-2]
colnames(descriptives_RT_Raw)[-1:-2] <- paste("Reaction Time.", c_names)

c_names <- colnames(descriptives_Errors)[-1:-2]
colnames(descriptives_Errors)[-1:-2] <- paste("Errors.", c_names)

dscr_er <- inner_join(descriptives_RT_Raw[,1:4], descriptives_Errors[,1:4],
                      by = c("Evaluation", "CL"))

table <- nice_table(dscr_er, separate.header = TRUE)
#table
save_as_docx(table, path = "TablesFigures/Table A2 - Descriptives WM Performance.docx")


## Across evaluation, CL, condition blocks, and trial blocks
c_names <- colnames(descriptives_RT_Raw_all)[-1:-4]
colnames(descriptives_RT_Raw_all)[-1:-4] <- paste("Reaction Time.", c_names)

c_names <- colnames(descriptives_Errors_all)[-1:-4]
colnames(descriptives_Errors_all)[-1:-4] <- paste("Errors.", c_names)

dscr_er <- inner_join(descriptives_RT_Raw_all[,1:6], descriptives_Errors_all[,1:6], 
                      by = c("Evaluation", "CL", "block", "trial_block"))

table <- nice_table(dscr_er, separate.header = TRUE)#, italics = seq(dscr_er))
#table

save_as_docx(table, path = "TablesFigures/Descriptives WM Performance across blocks.docx")
##
```

## Eustress and Distress (ADES)

Eustress

```{r}

descriptives <- agg_df %>% group_by(Evaluation, CL) %>% 
  dplyr::summarise(M = mean(Eustress,na.rm = TRUE), SD = sd(Eustress,na.rm = TRUE), n = n()) %>% 
  mutate(SE = SD / sqrt(n),
         CI_lower = M - qt(1 - (0.05 / 2), n - 1) * SE,
         CI_upper = M + qt(1 - (0.05 / 2), n - 1) * SE)

descriptives_Eustress <- cbind(descriptives[,1:2],round(descriptives[,3:8],2))
descriptives_Eustress
```

Distress

```{r}
descriptives <- agg_df %>% group_by(Evaluation, CL) %>% 
  dplyr::summarise(M = mean(Distress,na.rm = TRUE), SD = sd(Distress,na.rm = TRUE), n = n()) %>% 
  mutate(SE = SD / sqrt(n),
         CI_lower = M - qt(1 - (0.05 / 2), n - 1) * SE,
         CI_upper = M + qt(1 - (0.05 / 2), n - 1) * SE)

descriptives_Distress <- cbind(descriptives[,1:2],round(descriptives[,3:8],2))
descriptives_Distress
```

*Merge Variables*

```{r}
c_names <- colnames(descriptives_Eustress)[-1:-2]
colnames(descriptives_Eustress)[-1:-2] <- paste("Eustress.", c_names)

c_names <- colnames(descriptives_Distress)[-1:-2]
colnames(descriptives_Distress)[-1:-2] <- paste("Distress.", c_names)

dscr <- inner_join(descriptives_Eustress[,1:4], descriptives_Distress[,1:4],
                      by = c("Evaluation", "CL"))

table <- nice_table(dscr, separate.header = TRUE)#, italics = seq(dscr_er))
#table

save_as_docx(table, path = "TablesFigures/Table A4 - Descriptives ADES.docx")
```

## NASA-TLX

Mental

```{r}
descriptives <- agg_df %>% group_by(Evaluation, CL) %>% 
  dplyr::summarise(M = mean(Mental,na.rm = TRUE), SD = sd(Mental,na.rm = TRUE), n = n()) %>% 
  mutate(SE = SD / sqrt(n),
         CI_lower = M - qt(1 - (0.05 / 2), n - 1) * SE,
         CI_upper = M + qt(1 - (0.05 / 2), n - 1) * SE)

descriptives_Mental <- cbind(descriptives[,1:2],round(descriptives[,3:8],2))
descriptives_Mental
```

Temporal

```{r}
descriptives <- agg_df %>% group_by(Evaluation, CL) %>% 
  dplyr::summarise(M = mean(Temporal,na.rm = TRUE), SD = sd(Temporal,na.rm = TRUE), n = n()) %>% 
  mutate(SE = SD / sqrt(n),
         CI_lower = M - qt(1 - (0.05 / 2), n - 1) * SE,
         CI_upper = M + qt(1 - (0.05 / 2), n - 1) * SE)

descriptives_Temporal <- cbind(descriptives[,1:2],round(descriptives[,3:8],2))
descriptives_Temporal
```

Effort

```{r}
descriptives <- agg_df %>% group_by(Evaluation, CL) %>% 
  dplyr::summarise(M = mean(Effort,na.rm = TRUE), SD = sd(Effort,na.rm = TRUE), n = n()) %>% 
  mutate(SE = SD / sqrt(n),
         CI_lower = M - qt(1 - (0.05 / 2), n - 1) * SE,
         CI_upper = M + qt(1 - (0.05 / 2), n - 1) * SE)

descriptives_Effort <- cbind(descriptives[,1:2],round(descriptives[,3:8],2))
descriptives_Effort
```

Perceived Performance

```{r}
descriptives <- agg_df %>% group_by(Evaluation, CL) %>% 
  dplyr::summarise(M = mean(Performance,na.rm = TRUE), SD = sd(Performance,na.rm = TRUE), n = n()) %>% 
  mutate(SE = SD / sqrt(n),
         CI_lower = M - qt(1 - (0.05 / 2), n - 1) * SE,
         CI_upper = M + qt(1 - (0.05 / 2), n - 1) * SE)

descriptives_Performance <- cbind(descriptives[,1:2],round(descriptives[,3:8],2))
descriptives_Performance
```

Frustration

```{r}
descriptives <- agg_df %>% group_by(Evaluation, CL) %>% 
  dplyr::summarise(M = mean(Frustration,na.rm = TRUE), SD = sd(Frustration,na.rm = TRUE), n = n()) %>% 
  mutate(SE = SD / sqrt(n),
         CI_lower = M - qt(1 - (0.05 / 2), n - 1) * SE,
         CI_upper = M + qt(1 - (0.05 / 2), n - 1) * SE)

descriptives_Frustration <- cbind(descriptives[,1:2],round(descriptives[,3:8],2))
descriptives_Frustration
```

*Merge*

```{r}
c_names <- colnames(descriptives_Mental)[-1:-2]
colnames(descriptives_Mental)[-1:-2] <- paste("Mental Demand.", c_names)

c_names <- colnames(descriptives_Temporal)[-1:-2]
colnames(descriptives_Temporal)[-1:-2] <- paste("Temporal Demand.", c_names)

c_names <- colnames(descriptives_Effort)[-1:-2]
colnames(descriptives_Effort)[-1:-2] <- paste("Effort.", c_names)

c_names <- colnames(descriptives_Performance)[-1:-2]
colnames(descriptives_Performance)[-1:-2] <- paste("Performance.", c_names)

c_names <- colnames(descriptives_Frustration)[-1:-2]
colnames(descriptives_Frustration)[-1:-2] <- paste("Frustration.", c_names)

dscr_nasa <- inner_join(descriptives_Mental[,1:4], descriptives_Temporal[,1:4],
                      by = c("Evaluation", "CL")) %>%
  inner_join(descriptives_Effort[,1:4], by = c("Evaluation", "CL")) %>%
  inner_join(descriptives_Performance[,1:4], by = c("Evaluation", "CL")) %>%
  inner_join(descriptives_Frustration[,1:4], by = c("Evaluation", "CL"))

table <- nice_table(dscr_nasa, separate.header = TRUE)#, italics = seq(dscr_er))

save_as_docx(table, path = "TablesFigures/Table A1 - Descriptives NASA.docx")
```

# Visualisation

Import customised raincloud plot functions

```{r}
source("raincloud_function.R")
```

## Working Memory Performance

Errors

```{r, fig.width=7, fig.height=5}
errors_df <- raincloud_prepare_data(data = agg_df,
                                id_variable = "ID",
                                y_variable = "Errors",
                                within_factor = "Evaluation",
                                between_factor = "CL",
                                within_levels = c(0,1),
                                between_levels = c("low", "high"))

errors_plot <-raincloud_plot(data = errors_df$data,
               within_levels = c("Control", "Evaluation"),
               within_label = "",
               between_levels = c("Low", "High"),
               violins = T,
               boxplot = T,
               between_annotations = "bottom",
               colors = c(c1_low, c2_high)) +
  xlab("Cognitive Load") + ylab("Errors")

errors_plot
```

Reaction Time

```{r}
rt_df <- raincloud_prepare_data(data = agg_df,
                                id_variable = "ID",
                                y_variable = "RT_Raw",
                                within_factor = "Evaluation",
                                between_factor = "CL",
                                within_levels = c(0,1),
                                between_levels = c("low", "high"))

rt_plot <-raincloud_plot(data = rt_df$data,
               within_levels = c("Control", "Evaluation"),
               within_label = "",
               between_levels = c("Low", "High"),
               violins = T,
               boxplot = T,
               between_annotations = "bottom",
               colors = c(c1_low, c2_high)) +
  xlab("Cognitive Load") + ylab("Reaction Time")
```

*Merge plots*

```{r, fig.width=8, fig.height=4}
combined_plot <- (rt_plot | errors_plot) +
  plot_annotation(tag_levels = 'A') +
  plot_layout(guides = "collect") &
  theme(plot.tag = element_text(face = "bold"),
        legend.position='bottom')

# Display the combined plot
print(combined_plot)
ggsave("TablesFigures/Figure A1 - WM Performance Raincloud_plot.jpeg",dpi=600, w= 9.5, h = 4)
```

## Perceived Stress (ADES)

Eustress

```{r}
eustress_df <- raincloud_prepare_data(data = agg_df,
                                id_variable = "ID",
                                y_variable = "Eustress",
                                within_factor = "Evaluation",
                                between_factor = "CL",
                                within_levels = c(0,1),
                                between_levels = c("low", "high"))

eustress_plot <-raincloud_plot(data = eustress_df$data,
               within_levels = c("Control", "Evaluation"),
               within_label = "",
               between_levels = c("Low", "High"),
               violins = T,
               boxplot = T,
               between_annotations = "bottom",
               colors = c(c1_low, c2_high)) +
  xlab("Cognitive Load") + ylab("Eustress")
```

Distress

```{r}
distress_df <- raincloud_prepare_data(data = agg_df,
                                id_variable = "ID",
                                y_variable = "Distress",
                                within_factor = "Evaluation",
                                between_factor = "CL",
                                within_levels = c(0,1),
                                between_levels = c("low", "high"))

distress_plot <-raincloud_plot(data = distress_df$data,
               within_levels = c("Control", "Evaluation"),
               within_label = "",
               between_levels = c("Low", "High"),
               violins = T,
               boxplot = T,
               between_annotations = "bottom",
               colors = c(c1_low, c2_high)) +
  xlab("Cognitive Load") + ylab("Distress")
```

*Merge plots*

```{r, fig.width=10, fig.height=5}
combined_plot <- (eustress_plot | distress_plot) +
  plot_annotation(tag_levels = 'A') +
  plot_layout(guides = "collect") &
  theme(plot.tag = element_text(face = "bold"),
        legend.position='bottom')

# Display the combined plot
print(combined_plot)
ggsave("TablesFigures/Figure A2 - ADES Raincloud_plot.jpeg",dpi=600, w= 9.5, h = 4)
```

## Mental Demand

```{r, fig.width=7, fig.height=5}
meanp_size = 3
p_size = 2

mental_df <- raincloud_prepare_data(data = agg_df,
                                id_variable = "ID",
                                y_variable = "Mental",
                                within_factor = "CL",
                                between_factor = "Evaluation",
                                within_levels = c("low", "high"),
                                between_levels = c(0,1))

mental_plot <-raincloud_plot(data = mental_df$data,
               within_levels = c("Low", "High"),
               within_label = "Cognitive Load",
               between_levels = c("Control", "Evaluation"),
               violins = T,
               boxplot = T,
               between_annotations = "bottom",
               colors = c(c1_low, c2_high)) +
  xlab("Social Evaluation") + ylab("Mental Demand")

print(mental_plot)
ggsave("TablesFigures/Figure 2 - Mental Demand raincloud-plot.jpeg",dpi=600, w= 7, h = 5)
```
