**Import libraries using a reproducible approach**

```{r}
pkgs <- c("tidyverse",
          "ggpubr",
          "lme4",
          "lmerTest",
          "rstatix",
          "car",
          "modelbased")

lapply(pkgs, library, character.only=TRUE)


options(es.use_symbols = TRUE)
```

### Data Preparation

```{r}
main_df <- read_csv("../Data/clean_data/main_df.csv", show_col_types = FALSE)
main_df$ID <- factor(main_df$ID)
main_df$Evaluation <- factor(main_df$Evaluation)
main_df$CL <- factor(main_df$CL, levels = c("low","high"))
main_df$block <- factor(main_df$block)
main_df$trial_block <- factor(main_df$trial_block)

agg_df <- read_csv("../Data/clean_data/agg_df.csv", show_col_types = FALSE)
agg_df$ID <- factor(agg_df$ID)
agg_df$Evaluation <- factor(agg_df$Evaluation)
agg_df$CL <- factor(agg_df$CL, levels = c("low","high"))

all_trials_df <- read_csv("../Data/clean_data/all_trials_df.csv", show_col_types = FALSE)
all_trials_df$ID <- factor(all_trials_df$ID)
all_trials_df$Evaluation <- factor(all_trials_df$Evaluation)
all_trials_df$CL <- factor(all_trials_df$CL, levels = c("low","high"))
all_trials_df$block <- factor(all_trials_df$block)
all_trials_df$trial_block <- factor(all_trials_df$trial_block)
```

# Sensitivity Analyses

### Three different subsets:

a)  Excluding outliers

```{r}
outliers_rt <- read_csv("../Data/clean_data/Outliers_RT.csv", show_col_types = FALSE)
outliers_rt <- sapply(outliers_rt$ID,as.character)

outliers_errors <- read_csv("../Data/clean_data/Outliers_errors.csv", show_col_types = FALSE)
outliers_errors<- sapply(outliers_errors$ID,as.character)
```

b)  Excluding male participants

```{r}
excl_males <- c("588210","93756","069369","765713","017709")
```

c)  Excluding participants who failed the manipulation check (i.e., no increase in EDA & distrusting the deception)

```{r}
excl_mcheck <- c("588210", "40710", "848371")
```

## Sensitivity Analyses for Reaction Time

### Excluding outliers

```{r}
agg_df1 <- subset(agg_df,!(ID %in% outliers_rt))
main_df1 <- subset(main_df, !(ID %in% outliers_rt))

aov <- anova_test(data = agg_df1, RT_Raw ~ CL*Evaluation + Error(ID/(CL+Evaluation)), type =3,
                  effect.size="pes")
get_anova_table(aov)

m4 <- lmer(scale(RT_Raw) ~ block + trial_block + CL+Evaluation + (CL+Evaluation|ID),
           data=main_df1, REML = T)
summary(m4)
```

No differences in direction of the effect

### Excluding male participants

```{r}
agg_df1 <- subset(agg_df,!(ID %in% excl_males))
main_df1 <- subset(main_df, !(ID %in% excl_males))

aov <- anova_test(data = agg_df1, RT_Raw ~ CL*Evaluation + Error(ID/(CL+Evaluation)), type =3,
                  effect.size="pes")
get_anova_table(aov)

m4 <- lmer(scale(RT_Raw) ~ block + trial_block + CL+Evaluation + (CL+Evaluation|ID),
           data=main_df1, REML = T)
summary(m4)
```

No differences in direction of the effect

### Excluding participants who failed the manipulation check

```{r}
agg_df1 <- subset(agg_df,!(ID %in% excl_mcheck))
main_df1 <- subset(main_df, !(ID %in% excl_mcheck))

aov <- anova_test(data = agg_df1, RT_Raw ~ CL*Evaluation + Error(ID/(CL+Evaluation)), type =3,
                  effect.size="pes")
get_anova_table(aov)

m4 <- lmer(scale(RT_Raw) ~ block + trial_block + CL+Evaluation + (CL+Evaluation|ID),
           data=main_df1, REML = T)
summary(m4)
```

No differences in direction of the effect

## Sensitivity Analyses for errors

### Excluding outliers

```{r}
all_trials_df1 <- subset(all_trials_df,!(ID %in% outliers_errors))

m4 <- glmer(Errors ~ block + trial_block + CL + Evaluation + (1|ID),
           data=all_trials_df1, family = binomial)
summary(m4)
```

No differences in direction of the effect

### Exclude males

```{r}
all_trials_df1 <- subset(all_trials_df,!(ID %in% excl_males))

m4 <- glmer(Errors ~ block + trial_block + CL + Evaluation + (1|ID),
            data=all_trials_df1, family = binomial)
summary(m4)
```

No differences in direction of the effect

### Excluding participants who failed the manipulation check

```{r}
all_trials_df1 <- subset(all_trials_df,!(ID %in% excl_mcheck))

m4 <- glmer(Errors ~ block + trial_block + CL + Evaluation + (1|ID),
            data=all_trials_df1, family = binomial)
summary(m4)
```

No differences in direction of the effect
